Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-03-31 paper.qmd
renamed paper.R1.qmd to paper.qmd

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: 
  - name: Caroline B. Smith
    affiliation:
     - id: wsu
       department: Department of Anthropology
       name: Washington State University
  - name: Edward H. Hagen
    affiliation:
     - ref: wsu
date: today
format:
  html:
    toc: true
    embed-resources: true
  # docx:
  #   number-sections: true
execute:
  echo: false
  warning: false
csl: apa.csl
bibliography: paper.bib
crossref:
  custom:
    - kind: float
      reference-prefix: Figure S
      key: sfig
      space-before-numbering: false
    - kind: float
      reference-prefix: Table S
      key: stbl
      space-before-numbering: false
---

@@

Figure3 <- forestplot(
  mwbc,
  mwbc_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  theme_minimal(17) +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))

ggsave("Figures/Figure3.pdf", Figure3, width = 14, height = 7)

Figure3

```

@@

Figure4 <- forestplot(
  m_energy,
  m_energy_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  theme_minimal(17) +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))

ggsave("Figures/Figure4.pdf", Figure4, width = 14, height = 7)

Figure4 
```

@@

Figure5 <- forestplot(
  m_protein,
  m_protein_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  theme_minimal(17) +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))

ggsave("Figures/Figure5.pdf", Figure4, width = 14, height = 7)

Figure5 
```

@@

### Models of mating success with socioeconomic, health, hormone, and physical activity controls

::: {#sfig-lifetime}
```{r}
#| fig-height: 10
forestplot2(m_lifetime, msoc1, mheal1, mphys1, mhor1, title = "Lifetime Number of Sexual Partners")
```

Models of lifetime number of sex partners.
:::

::: {#sfig-year}
```{r}
#| fig-height: 10
forestplot2(m_pastyear, msoc2,mheal2, mphys2, mhor2, title = "Past Year Number of Sexual Partners")
```

Models past year sex partners.
:::

::: {#sfig-agefirstsex}
```{r}
#| fig-height: 10
forestplot2(m_agefirst, msoc3, mheal3, mphys3, mhor3, title = "Age at First Sex")
```

Models of age at first sex
:::

::: {#sfig-partnered}
```{r}
#| fig-height: 10
forestplot2(m_partnered, msoc4, mheal4, mphys4, mhor4, title = "Currently Partnered")
```

Models of partnered status
:::

@@

::: {#sfig-tradeoff}
```{r}
plot_lifetime_coefs
```

@@

::: {#sfig-cor}
```{r}
ggcorrplot(cor_mat_cors, hc.order = T, hc.method = 'ward.D', title = 'Both sexes')
```

@@

::: {#sfig-fcor}
```{r}
ggcorrplot(cor_mat_cors_f, hc.order = T, hc.method = 'ward.D', title = 'Females')
```

@@

::: {#sfig-mcor}
```{r}
ggcorrplot(cor_mat_cors_m, hc.order = T, hc.method = 'ward.D', title = 'Males')
```

>>>>

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: 
  - name: Caroline B. Smith
    affiliation:
     - id: wsu
       department: Department of Anthropology
       name: Washington State University
  - name: Edward H. Hagen
    affiliation:
     - ref: wsu
date: today
lightbox: auto
format:
  html:
    toc: true
    embed-resources: true
  # docx:
  #   number-sections: true
  #   fig-format: pdf
execute:
  echo: false
  warning: false
csl: apa.csl
bibliography: paper.bib
crossref:
  custom:
    - kind: float
      reference-prefix: Figure S
      key: sfig
      space-before-numbering: false
    - kind: float
      reference-prefix: Table S
      key: stbl
      space-before-numbering: false
---

@@

plot_immune <- forestplot(
  mwbc,
  mwbc_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  theme_minimal(17) +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))

ggsave("Figures/plot_immune.pdf", plot_immune, width = 14, height = 7)

plot_immune
```

@@

plot_energy <- forestplot(
  m_energy,
  m_energy_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  theme_minimal(17) +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))

ggsave("Figures/plot_energy.pdf", plot_energy, width = 14, height = 7)

plot_energy 
```

@@

plot_protein <- forestplot(
  m_protein,
  m_protein_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  theme_minimal(17) +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))

ggsave("Figures/plot_protein.pdf", plot_protein, width = 14, height = 7)

plot_protein 
```

@@

### Models of mating success with anthropometric, socioeconomic, health, hormone, and physical activity controls

::: {#sfig-allcoefs}
```{r}
plot_allcoefs
```

Coefficients from all models.
:::

@@

::: {#sfig-tradeoff}
```{r}
#| fig-width: 11
plot_lifetime_coefs
```

@@

::: {#sfig-cor}
```{r}
cor_bothsexes <- ggcorrplot(cor_mat_cors, hc.order = T, hc.method = 'ward.D', title = 'Both sexes')
ggsave("Figures/cor_bothsexes.pdf", cor_bothsexes)
cor_bothsexes
```

@@

::: {#sfig-fcor}
```{r}
cor_females <- ggcorrplot(cor_mat_cors_f, hc.order = T, hc.method = 'ward.D', title = 'Females')
ggsave("Figures/cor_females.pdf", cor_females)
cor_females
```

@@

::: {#sfig-mcor}
```{r}
cor_males <- ggcorrplot(cor_mat_cors_m, hc.order = T, hc.method = 'ward.D', title = 'Males')
ggsave("Figures/cor_males.pdf", cor_males)
cor_males
```
